### 2014-03-20 paper/tubes.tex
paper work, adding a new figure

\section{A Series of Tubes - A Tool for Tube Design}

We created a tool which makers can use to create tube-powered interfaces in arbitrary 3D models.  This tool allows designers to brush over the surface of their model to select exterior connection points of their tubes (see Figure \ref{fig:tool-process-interior}) or to import vector art describing the tubes' interior paths (see Figure \ref{fig:tool-process-exterior}).  Once the user's selections are made, we create a complete routing using either the exterior connection point method (A*) or the interior path method (graph edge creation, Euler circuit generation).  We thicken our routing and use a physics-based rod simulation to minimize bending energy of tubes.  We also apply templates where appropriate (e.g., 3D cross-overs for tubes that intersect in the plane).  The resultant routing is subtracted from the original mesh.  The modified mesh can then be 3D printed.

Our tool is implemented as a part of Meshmixer, a consumer mesh editing tool, in C++.

@@

To create tubes in which the location and shape of exterior connection points matters, we first allow users to select the connection points on the mesh's surface using a brush. Our tool then creates an initial shortest-path routing using A* to estimate the routed distance between points.  This routing is used to create a rod; we run physics-based simulation steps on the rod to minimize its bending energy (and thereby minimize the bend radius of the tubes).

@@

\subsubsection{Routing}

@@

Physical Simulation :

How does it actually work? \valkyrie{Ryan?}

Bend Minimization

In order to force our simulated rods away from the surface of the mesh, we create ``wind'' pushing inward from the exterior of the mesh.  This wind pushes the tube away from the surface.

\subsubsection{Tubes with Multiple Endpoints}

To allow designers to create tubes with multiple endpoints (like the star topologies in Figure \ref{fig:toys}), we ....???? \valkyrie{create 0-size mesh points in the center of the object, to which we attach one end of every tube?}

@@

A user can import a vector graphics file (such as SVG) describing the path she desires for her tubes.  We create a graph based on this input data, then add edges to make it connected and semi-Eulerian.  We create an Euler tour on the modified graph, and thicken the path to create tubes.  3D templates are used to resolve tube crossings in the plane.

@@

Now to remove our temporary edge and make the graph semi-Eulerian instead of Eulerian, let $E' = E' \setminus e_{temp}$.

\valkyrie{does the proof of this theorem belong in the paper, or in the appendix?  we can push it back there if need be, although it's not super long.}
\begin{theorem}
 $G' = (V, E')$ is a connected, semi-Eulerian graph for which $E \subseteq E'$. \valkyrie{why is there such a huge space after this paragraph?}
\end{theorem}
\begin{proof}
$E \subseteq E'$ : we never remove edges from $E$ in our algorithm.  $\therefore E \subseteq E'$.

$G' = (V, E')$ is connected : if $G'$ is not connected, $\exists G_i = (V_i, E_i) \subset G', u \in V_i, v\in V \setminus V_i$ s.t. $u$ is not reachable from $v$.  $G_i \not\in G_{dis}$, because we create edges connecting $G_j, G_k \forall G_j, G_k \in G_{dis}$ and only remove an edge $e_{dupe} = (u, v)$ from $E_{conn}$ once we determine that $u$ is reachable from $v$ along edges $E' \cup E_{conn-min}$.  $\therefore G_i \not\in G_{dis}$.  This implies that $G_i$ was not initially disconnected from $G$, because by definition $G_{dis}$ is the set of all disconnected subgraphs of $G$.  We cannot have disconnected $G_i$ from $G$ because $E \subseteq E'$.  Thus, a contradiction.  $\therefore G' = (V, E')$ is connected.

$G' = (V, E')$ is semi-Eulerian : Each edge $e$ in our minimum weight matching connects a unique pair of vertices $v_i, v_j \in V_{odd}$ by the definition of minimum weight matching.  Each edge $e = (v_i, v_j) \in E_{circuit-min}$ adds one to the degree of $v_i$ and $v_j$, causing them to be of even degree. $|V_{odd}| \% 2 = 0$ by the handshake lemma, $\therefore$ all edges can be paired.  When we remove $e_{temp} = (start, end)$ from $E'$, we cause those vertices, which were of even degree by the above process, to be of odd degree.  Thus, all vertices except $start$ and $end$ (which are of odd degree) are of even degree.  $\therefore G'$ is semi-Eulerian.
\end{proof}

@@

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/templates.jpg}
\caption{When edges intersect in the plane (a), we match them to the nearest of our several intersection templates (b) to create 3D paths that do not interfere with each other.}
\label{fig:templates}
\end{figure}

\subsubsection{Edges that Intersect in the Plane}
Once we have a tour, we must resolve tubes that intersect in the plane.  Because we have a 3-dimensional canvas in which to work, we can push overlapping paths into the third dimension.

To detect intersecting edges, we \valkyrie{I'm not sure what we do.}.  We also consider edges at nodes with degree $>2$, as these edges are considered to cross.  When intersections have been detected, we match one of several templates to the affected edges (see Figure \ref{fig:templates}) using a nearest neighbors technique.  Our templates are parameterized, so the templates can be modified to accommodate precise intersection characteristics.

\valkyrie{For now, we just let them intersect.  The angel hair EL wire is thin enough that we don't actually care.}

@@

How we actually cut stuff and make tubes happen. \valkyrie{Ryan?}  We have to actually respect whatever shapes people drew on the surface in the case of the exterior connection tubes (I mean, ideally, we would do a loft operation here).

>>>>

\section{A Series of Tubes - A Tool for Pipe Design}

To allow makers to design novel objects with pipe-powered interfaces, we created a tool for use on arbitrary 3D models.  This tool allows designers to select exterior connection points of their pipes (see Figure \ref{fig:tool-process-interior}) or to import vector art describing the pipes' interior paths (see Figure \ref{fig:tool-process-exterior}).  Once the maker's selections are made, we create a complete routing using either the exterior connection point method (A*, physical simulation) or the interior path method (graph edge creation, Euler circuit generation).  We thicken our routing to create pipes. \valkyrie{We also apply templates where appropriate (e.g., 3D cross-overs for tubes that intersect in the plane).}  The resultant pipes are subtracted from the original mesh, which can then be 3D printed.

Our tool is implemented as a part of Meshmixer, a consumer 3D mesh editing tool, in C++.

@@

Designing objects which, for example, are touch sensitive in particular areas or need to integrate with existing electronics, requires precise location and sizing of pipe endpoints.  The interior of these pipes should have as large a bending radius as possible so that post-print insertion of solid or viscous media (like wire or paint) is easier.

To create pipes in which the location and shape of exterior connection points matters, we first allow makers to select the connection points on the mesh's surface using a brush. Our tool then creates an initial shortest-path routing using A* to estimate the routed distance between points.  This routing is used to create a rod; we run physics-based simulation steps on the rod to minimize its bending energy (and thereby minimize the bend radius of the tubes).

@@

\subsubsection{Routing and Physical Simulation}

@@

To allow for easiest insertion of media post-print, our physical simulation step minimizes the bend radius of the generated rods.  In order to force our simulated rods away from the surface of the mesh, we create ``wind'' pushing inward from the exterior of the mesh.  This wind keeps the resulting pipe away from the surface. \valkyrie{Ryan: How does it actually work?}

\subsubsection{Tubes with Multiple Endpoints}
For the creation of tubes with multiple endpoints, for example the star topologies in Figure \ref{fig:toys} or tree topologies, makers can select interior faces of existing pipes as endpoints, and thereby create pipe networks by hand.  We do not currently offer any pipe network manipulation tools.

\valkyrie{To allow designers to create tubes with multiple endpoints (like the star topologies in Figure \ref{fig:toys}), we create 0-size mesh points in the center of the object, to which we attach one end of every tube?}

\subsubsection{Tubes with Non-Round Endpoints}
Our tool does not explicitly allow makers to design the shape of their tubes' endpoints.  However, the larger Meshmixer package does allow brushing arbitrary shapes onto the surface and extruding them inward, as in Figure \ref{fig:meshmixer-endpoint}. \valkyrie{should we have a figure about this?  I  don't know how to describe it really, but we also didn't build it as a part of our tool.}

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/meshmixer-endpoint.png}
\caption{After creating a tube, a maker can select a surface shape using a brush (a).  She can then extrude her selection inward (b).}
\label{fig:meshmixer-endpoint}
\end{figure}

@@

Neon signs, as in Figure \ref{fig:tool-process-interior}(d), require a single long path that passes through many desired edges: for example, in our UIST sign, the path must pass through all the edges that comprise the word ``UIST''.  To allow makers to create novel neon signs, as well as similar objects that require design of the pipe's interior path, we built a tool which leverages graph theory to generate this single long path.

A maker can import a vector graphics file (such as SVG) describing the path she desires for her pipes.  We create a graph based on this input data, then add edges to make it connected and semi-Eulerian.  We create an Euler tour on the modified graph, and thicken the path to create pipes.  \valkyrie{3D templates are used to resolve tube crossings in the plane.}  We cut these pipes from a generated block mesh large enough to hold them.

@@

Now to remove our temporary edge and make the graph semi-Eulerian instead of Eulerian, let $E' = E' \setminus e_{temp}$.
{
\renewcommand{\thetheorem}{\ref{thm:graphness}}
\begin{theorem}
 $G' = (V, E')$ is a connected, semi-Eulerian graph for which $E \subseteq E'$.
\end{theorem}
\addtocounter{theorem}{-1}
}
\begin{proof}
See appendix.
\end{proof}

@@

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/templates.jpg}
\caption{\valkyrie{When edges intersect in the plane (a), we match them to the nearest of our several intersection templates (b) to create 3D paths that do not interfere with each other.}}
\label{fig:templates}
\end{figure}

\subsubsection{Edges that Intersect in the Plane}
We do not currently redirect edges that intersect in the plane.  Because we have a 3-dimensional canvas in which to work, it would be possible to push overlapping paths into the third dimension, however the angel hair EL wire we have used for our prototypes is so thin as to make this unnecessary.

\valkyrie{Once we have a tour, we must resolve tubes that intersect in the plane.  Because we have a 3-dimensional canvas in which to work, we can push overlapping paths into the third dimension.

To detect intersecting edges, we \valkyrie{I'm not sure what we do.}.  We also consider edges at nodes with degree $>2$, as these edges are considered to cross.  When intersections have been detected, we match one of several templates to the affected edges (see Figure \ref{fig:templates}) using a nearest neighbors technique.  Our templates are parameterized, so the templates can be modified to accommodate precise intersection characteristics.}

@@

How we actually cut stuff and make tubes happen. \valkyrie{Ryan?}
